Removing nonlinear batch effects using adversarial deep neural networks

### 2019-02-13 thesis.tex
Fix tables
Put figures in the right sections

\documentclass[notitlepage]{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage[square,numbers]{natbib}
\usepackage[nomarkers]{endfloat}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,footskip=0.25in]{geometry}
\linespread{1.5}
\bibliographystyle{unsrtnat}
% TODO: increase spacing, decrease margins.

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/adjuster_workflow}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/batch_accuracy}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mmd}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mnist}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mse}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/pca}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/training_loss}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/true_class_accuracy}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/tsne}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}

@@

@@

>>>>

\documentclass[notitlepage]{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage[square,numbers]{natbib}
\usepackage[nomarkers,nolists]{endfloat}
\renewcommand{\efloatseparator}{\mbox{}} % multiple figures per page
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,footskip=0.25in]{geometry}
\usepackage{csvsimple}
\linespread{1.5}
\bibliographystyle{unsrtnat}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/adjuster_workflow}
	\caption{\textbf{Batch adjustment justification and steps} (a) When measurements are collected from a sample ($X$), systematic effects ($H$) also affect the measurements. (b) If data from the same sample $X$ is measured under two different conditions, $H_1$ and $H_2$, we may obtain slightly different measurements. (c) In orer to normalize batches of data relative to one another, we first estimate the effect of the hidden variables based on differences in measurements between batches. (d) Second, we remove the estimated effects in order to normalize the batches relative to one another.}
	\label{fig:workflow}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{\textbf{Network architecture} of Confounded. Data with batch effects (represented by different colors) are input into an autoencoder. The output of the autoencoder is classified by a discriminator network based on batch. The autoencoder is then penalized based on the success of the discriminator. Over time, the autoencoder learns to output a faithful representation of the data without signal due to batch.}
	\label{fig:network}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/training_loss}
	\caption{Autoencoder and discriminator loss over time for one run of Confounded. Over the course of training, the autoencoder more faithfully replicates the input data. The autoencoder also seems to introduce noise (see around iteration 3100) in response to the discriminator's slight improvements.}
	\label{fig:training_loss}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mnist}
	\caption{\textbf{MNIST handwritten digits} (a) before any adjustment, (b), with artificial noise added, (c) adjusted for noise by ComBat, and (d) adjusted for noise by Confounded. Although Confounded seems to remove more noise from the background and make it look more like the original background, it struggles in some cases to accurately replicate the input data.}
	\label{fig:mnist}
\end{figure}\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/pca}
	\caption{\textbf{Principal components analysis} (PCA) of the GSE37199 dataset before and after batch adjustment with various adjusters.}
	\label{fig:pca}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/tsne}
	\caption{\textbf{T-distributed Stochastic Neighbor Embedding} (t-SNE) plot for the GSE37199 dataset before and after adjustment with several algorithms.}
	\label{fig:tsne}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mse}
	\caption{\textbf{Mean squared error} (MSE) between the data prior to and after adjustment with various algorithms.}
	\label{fig:mse}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mmd}
	\caption{\textbf{Maximum mean discrepancy} (MMD) between different batches. In cases with more than two batches, MMD is computed pairwise between each batch and averaged.}
	\label{fig:mmd}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/batch_accuracy}
	\caption{\textbf{Batch classification accuracy} Accuracies for batch classification for 4-fold cross validation repeated 10 times for several classifiers.}
	\label{fig:batch}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/batch.csv}
	\caption{Batch classification accuracy}
	\label{tab:batch}
\end{table}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/true_class_accuracy}
	\caption{\textbf{True class classification accuracy} for several datasets and adjusters.}
	\label{fig:true_class}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/true_class.csv}
	\caption{True class classification accuracies}
	\label{tab:true_class}
\end{table}
